Supplementary Figure 8

### 2018-05-15 inst/supp_figure4c/supp_figure4c.Rmd
updating all paths to figure numbers
fixing figure labels in Rmds

---
title: "Supplementary Figure 4b"
subtitle: "CCND1 expression in PC3 stable cell lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Supplementary Figure 4b")

@@

<div class="caption">
Q-PCR showing cyclin D1 levels in PC3 miR34a asRNA over-expressing stable lines. The points represent the values obtained from each independant experiment (n = 6) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

>>>>

---
title: "Supplementary Figure 4c"
subtitle: "CCND1 expression in PC3 stable cell lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Supplementary Figure 4c")

@@

<div class="caption">
Q-PCR showing cyclin D1 levels in PC3 miR34a asRNA over-expressing stable lines. The points represent the values obtained from each independant experiment (n = 6). 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

### 2018-05-15 inst/supp_figure4d/supp_figure4d.Rmd
updating all paths to figure numbers
fixing figure labels in Rmds

---
title: "Supplementary Figure 4c"
subtitle: "CCND1 protein expression in PC3 stable lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

data <- getData("Supplementary Figure 4c")

@@

<div class="caption">
Western blot quantification showing cyclin D1 protein levels in PC3 miR34a asRNA over-expressing stable lines compared to mock. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

>>>>

---
title: "Supplementary Figure 4d"
subtitle: "CCND1 protein expression in PC3 stable lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

url <- "supp_figure4d/supp_figure4d_gel.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

data <- getData("Supplementary Figure 4d")

@@

<div class="caption">

Western blot quantification showing cyclin D1 protein levels in PC3 miR34a asRNA over-expressing stable lines compared to mock. The points represent the values obtained from each independant experiment (n = 3). 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

### 2018-05-15 inst/supp_figure5c/supp_figure5c.Rmd
fixing figure labels in Rmds

---
title: "Supplementary Figure 6"
subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Supplementary Figure 5c"
subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

### 2018-05-15 inst/supp_figure8/supp_figure8.Rmd
fixing figure labels in Rmds

---
title: "Supplementary Figure 6"
subtitle: "Lnc34a CAGE"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: flatly
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
editor_options: 
  chunk_output_type: console
---

@@

```{r}
nrCellLinesDown <- function() {
  getData("Supplementary Figure 6") %>% 
    pull(cell) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  getData("Supplementary Figure 6") %>%
    pull(cell) %>%
    unique()
}

RNAprepTable <- function() {
  getData("Supplementary Figure 6") %>%
    mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
    select(`rna extract`) %>%
    dplyr::count(`rna extract`)
}

localizationTable <- function() {
  getData("Supplementary Figure 6") %>%
    select(localization) %>%
    dplyr::count(localization)
}

@@

#cage data
cage <- getData("Supplementary Figure 6") %>%
  select(start, stop, level) %>%
  group_by(start, stop) %>%
  summarize(level = sum(level)) %>%
  ungroup() %>%
  arrange(desc(level)) %>%
  mutate(y = 1:n())

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Document 1a"][[1]])
# ggsave(
#   plot = g,
#   filename = path,
#   device = cairo_pdf,
#   height = 100,
#   width = 90,
#   units = "mm"
# )
```

>>>>

---
title: "Supplementary Figure 8"
subtitle: "Lnc34a CAGE"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: flatly
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
editor_options: 
  chunk_output_type: console
---

@@

```{r}
nrCellLinesDown <- function() {
  getData("Supplementary Figure 8") %>% 
    pull(cell) %>%
    unique() %>%
    length()
}

cellLinesInFinal <- function() {
  getData("Supplementary Figure 8") %>%
    pull(cell) %>%
    unique()
}

RNAprepTable <- function() {
  getData("Supplementary Figure 8") %>%
    mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
    select(`rna extract`) %>%
    dplyr::count(`rna extract`)
}

localizationTable <- function() {
  getData("Supplementary Figure 8") %>%
    select(localization) %>%
    dplyr::count(localization)
}

@@

#cage data
cage <- getData("Supplementary Figure 8") %>%
  select(start, stop, level) %>%
  group_by(start, stop) %>%
  summarize(level = sum(level)) %>%
  ungroup() %>%
  arrange(desc(level)) %>%
  mutate(y = 1:n())

@@

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Figure 8"][[1]])
# ggsave(
#   plot = g,
#   filename = path,
#   device = cairo_pdf,
#   height = 100,
#   width = 90,
#   units = "mm"
# )
```
